\documentclass{my_cv}
\usepackage[skins]{tcolorbox}

\begin{document}
\begin{multicols}{2}[
    \titletext{Vera}%
        {Kovaleva}%
        {}%
        {vekovaleva@edu.hse.ru}%
        {+7 916 062 06 74}%
        {Vera-Kovaleva}%
        {}%
]
\end{multicols}

\section{\faFileText}{SUMMARY}
Now I'm just in the process of learning, but I've already learned a lot. In the future I want to develop in the field of machine learning. My main qualities are diligence, perseverance and a desire to learn something new.

\begin{multicols}{2}
\section{\faPencil}{EXPERIENCE}

\work{Course Teacher / Sep 2022 - June 2023}%
    {MAXIMUM education - Moscow, Russia}%
    {I was preparing for the Unified State Exam in computer science and mathematics. The average score of my students in computer science is 81, in mathematics 78.}%
    {Python, Informatics, Maths}
    
\work{Math Tutor / May 2017 - June 2022}%
    {Private tutor - Moscow, Russia}%
    {I worked with three students from the 2th, 3th and 6th grades.}
    {Maths, Algebra, Geometry}
    
\section{\faList}{SKILLS}

\textbf{Programming languages:} Python, C++

\noindent\textbf{Tools:} NumPy, Pandas, Flask, PyTest, Docker

\noindent\textbf{Languages:} English, Russia

\noindent\textbf{Other:} Version control, Docker

\columnbreak

\section{\faPaintBrush}{PROJECTS}
    \school{Github CI / June 2023}%
    {- Build Github CI project for building and publishing PDF resume}%
    {- Using Docker, GitHub, workflows, LaTeX}
    \school{Telegram Bot / November 2022}%
    {- Made public Telegram Bot}%
    {- Using Python}

\section{\faGraduationCap}{EDUCATION}
    
\school{Higher School of Economics - Moscow, Russia}%
{BA in Applied Mathematics and Informatics}%
{Expected graduation: June 2026}

\section{\faStar}{VOLUNTEERING}

{I have been a member of Greenpeace for five years. I collect data on fires: shooting from a copter, digitization. I also went to a camp for young volunteers as a guide.}

\section{\faSoccerBallO}{ACTIVITIES / INTERESTS}

I am interested in art, I love theater and dancing most of all. Proactive about learning diverse things and happy to discuss those. Favorite physical activities would be gym and cycling.


\end{multicols}
\end{document}
